\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\geometry{a4paper, margin=1in}

\title{Doctor Visit Questionnaire}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Patient Information}

\begin{tabbing}
Name: \hspace{5cm} \= \underline{\hspace{10cm}} \\
Date of Birth: \> \underline{\hspace{10cm}} \\
Gender: \> \underline{\hspace{10cm}} \\
Contact Number: \> \underline{\hspace{10cm}} \\
Email Address: \> \underline{\hspace{10cm}} \\
\end{tabbing}

\section*{Visit Information}

\begin{tabbing}
Date of Visit: \hspace{5cm} \= \underline{\hspace{10cm}} \\
Reason for Visit: \> \underline{\hspace{25cm}} \\
\end{tabbing}

\section*{Medical History}

\begin{enumerate}[leftmargin=*, labelsep=1cm, align=left]
    \item Are you currently taking any medications? If yes, please list them: \\
    \underline{\hspace{25cm}}
    \item Do you have any allergies? If yes, please list them: \\
    \underline{\hspace{25cm}}
    \item Do you have any chronic conditions (e.g., diabetes, hypertension, asthma)? If yes, please specify: \\
    \underline{\hspace{25cm}}
    \item Have you had any surgeries or hospitalizations in the past? If yes, please provide details: \\
    \underline{\hspace{25cm}}
    \item Do you have any family history of significant medical conditions? If yes, please specify: \\
    \underline{\hspace{25cm}}
\end{enumerate}

\section*{Current Symptoms}

\begin{enumerate}[leftmargin=*, labelsep=1cm, align=left]
    \item What symptoms are you currently experiencing? Please describe in detail: \\
    \underline{\hspace{25cm}}
    \item When did these symptoms start? \underline{\hspace{10cm}}
    \item How severe are your symptoms on a scale from 1 (mild) to 10 (severe)? \underline{\hspace{2cm}}
    \item Have you noticed anything that makes your symptoms better or worse? If yes, please specify: \\
    \underline{\hspace{25cm}}
    \item Have you experienced these symptoms before? If yes, when? \\
    \underline{\hspace{25cm}}
\end{enumerate}

\section*{Lifestyle and Habits}

\begin{enumerate}[leftmargin=*, labelsep=1cm, align=left]
    \item Do you smoke? If yes, how much and how often? \underline{\hspace{10cm}}
    \item Do you consume alcohol? If yes, how much and how often? \underline{\hspace{10cm}}
    \item Do you exercise regularly? If yes, please describe your routine: \\
    \underline{\hspace{25cm}}
    \item How would you describe your diet? \underline{\hspace{10cm}}
    \item Do you have any other lifestyle habits that you think are relevant to your health? If yes, please describe: \\
    \underline{\hspace{25cm}}
\end{enumerate}

\section*{Additional Information}

\begin{enumerate}[leftmargin=*, labelsep=1cm, align=left]
    \item Is there anything else you would like to share with your doctor regarding your health or concerns? \\
    \underline{\hspace{25cm}}
\end{enumerate}

\vspace{1cm}
\begin{tabbing}
Patient Signature: \hspace{5cm} \= \underline{\hspace{10cm}} \\
Date: \> \underline{\hspace{10cm}}
\end{tabbing}

\vspace{1cm}
\noindent\textit{Please ensure all sections are completed to the best of your ability. This information will help your doctor provide you with the best possible care. Thank you!}

\end{document}
